### 2017-12-01 manuscript.rmd
made extended depth evolution contmap with BW diving spp at 20m, physalia at 0m

#####Vertical Habitat Evolution
```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of median depth of species"}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

>>>>

#####Vertical Habitat Evolution
```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```
```{r median_cont_BWincluded, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations."}
median_aggregate = aggregate(trimmed_SDdata$Depth,by=list(trimmed_SDdata$Species), FUN=median)
names(median_aggregate) = c("Spp","Depth")
median_aggregate[33,2] = 0
median_aggregate = median_aggregate[match(median_aggregate$Spp, ultratree$tip.label),]
median_depth = median_aggregate$Depth
names(median_depth) = median_aggregate$Spp
depthmap <- contMap(ultratree, median_depth, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```
